Micromechanism of Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with Void

### 2018-12-27 MDPI-Materials/2ndEdt/2ndEdt.tex
2nd Review

% Authors, for the paper (add full first names)
%\Author{Author \orcidA{}}
\Author{Ruicheng Feng$^{1,2}$\orcidA{}; Maomao Wang $^{1,*}$\orcidB{}; Haiyan Li$^{1,*}$; Yongnian Qi$^{1}$; Qi Wang$^{1}$; Zhiyuan Rui$^{1,2}$}
\address{
$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com(R.F.); 15620864891@163.com(M.W.); y5217@163.com(H.L.); 13893591491@163.com(Y.Q.); 18350122524@163.com(Q.W); zhiy\underline{ \ }rui@163.com(Z.R.)\\
% $^{2}$ \quad Key Laboratory of Digital Manufacturing Technology and Application, Ministry of Education, Lanzhou University of Technology, Lanzhou 730050, China
%*; e-mail@e-mail.com}
$^{2}$ \quad State Key Laboratory of Advanced Processing and Recycling of Non-ferrous Metals, Lanzhou University of Technology, Lanzhou 730050, China}
% Contact information of the corresponding author
\corres{Correspondence: 15620864891@163.com; y5217@163.com}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Cold deformation behavior of poly crystalline metallic material is affected by intrinsic defects such as dislocation, void, inclusion etc.  Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy cover about deformation behavior mainly on macro scale. This paper focuses on the cold deformation mechanism of two phase Ti-Al alloy at micro scale, and  the role of void  in deformation process. Molecular dynamics simulations were performed to study the evolution of micro structure of material under uniaxial tension. Interaction between spherical nano void with different size and position was also examined in the simulation. The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy. (2) void detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
% Keywords
\keyword{two phase Ti-Al alloy; void; molecular dynamics; cold deformation}

@@

\section{Introduction}
% and brittle rapture failure 
Titanium  aluminum based intermetallic alloys are promising high temperature structural materials because of their great corrosion resistance and strength at high temperature. Compared with nickle based alloy,  Ti-Al based alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components working at high temperature from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}. The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased from 30\% to 40\% \cite{Bewlay2016}. With the advancement of non-ferrous metallurgy, Ti-Al based alloy components have better economic efficiency than ever before. Ti-Al based alloys have good prospects for applications in aerospace and automobile industry. 
Poor ductility of Ti-Al alloy  at room temperature strongly affects the safety of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.

Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.  Much of the work has been performed on single phase $\gamma$-TiAl alloys and polysynthetically twinned crystals(PTC)\cite{Appel2016}. Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}.Mess research  cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}. 
void can be arose due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen. It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}. The initiation of crack at microscopic scale is a dynamic process, which results in difficulties on study of  mechanism about deformation and cracking, these defects are known playing a fundamental role in the deformation of materials. Multiscale method has been applied to study deformation behavior of polycrystal with single aluminum \cite{Groh2009} and titanium element respectively \cite{Liu2018}. It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.

The effect of void is another great concern about properties and deformation mechanism  of TiAl alloy.  Therefore, it is necessary to study the deformation response of intermetallics structural materials with the consideration of microstructure evolution. Previous study on void growth in single crystal $\gamma$-TiAl reveals that void with high volume fraction detracts yield strength \cite{Tang2014, Xu2011}. Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations, \cite{Jing2018a,Elkhateeb2018}, voids inside material are sources of dislocation and affects the properties of materials differently because of differences in size and position.  The deformation and fracture mechanisms in the duplex microstructure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}. It reveals that existence of voids alone may contribute to strain hardening because they are barriers to dislocation movement in ductile fcc structure metal\cite{Xiong2015}. However, few literature covers about deformation mechanism of two phase Ti-Al alloy and the role of void in atomic scale. Defects are inevitable as micro-pores and loosen from casting, and in the actual work environment with radiation. A lot of work carried out on the  effect of various defects on the behavior of different materials, showing that point defects may affect the properties of materials greatly. The mechanical performance of irradiated copper is affected by the interaction between irradiation and dislocation \cite{Kiener2011}. Vacancy concentration in single crystal and polycrystal Fe–40 at. Al bulk results in an increase of strength \cite{Yang1998}. Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are sensitive to the existence of void. Surface defects such as small notches can cause low and high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$-TiAl is also lowered by point defect \cite{Wu2016}. The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was reduced due to earlier crack initiation.  The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small cracks in the damaged zone. Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become an effective method to investigate micro deformation mechanism. Defects such as grain boundary, void and segregation play significant roles in the process of fracture \cite{Larsen2016}. This paper focus on the evolution of microstructure, tending to find out its connection to cold deformation behavior of two phase TiAl alloy. MD simulation including model creation and analysis method is given in Section \ref{section:method}, Results and discussion are in Section \ref{section:RD}.

@@

The interaction of particles in the material is determined by interatomic potential. Many reported simulation cases of deform and crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015,Zepeda-Ruiz2017,Fan2018a}. Embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study. The simulation is performed  with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}. We performed constant-pressure and constant-temperature (NPT) MD simulation at room temperature (298K). Definition of the potential is as following:

@@

\subsection{Model Creation of Crystalline}
\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{img/modeling}
	\caption{Unit cell of \rm{TiAl} (a), $\rm{Ti_3Al}$ (b) and two phase Ti-Al model (c)}
	\label{fig:tial-cell}
\end{figure}

@@

Two phase Ti-Al alloy is composed of $\gamma $-TiAl and $\alpha_2$-$\rm Ti_3Al$ has a fcc type cell with an $L1_0$ structure, and $\alpha_2$-$\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig. \ref{fig:tial-cell}, constructing parameters of the two type of unit cell are given by table \ref{tab:lattice_parameter}. Periodic boundary conditions (PBC) are applied along three directions, which makes polycrystal with periodic nanovoid structures. The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 460,000 atoms. The model contains 6 grains, with random shape and orientation were created with Voronoi method. Uniaxial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$. 
% In order to study the deformation mechanism of the two phase alloy and the effect of void, three types of models were created: Type-1.model without any void; Type-2. models with different size void inside $\alpha_2$ phase; Type-3. models with void at $\alpha_2-\gamma$ interface. \ref{tab:lattice_parameter}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure .
\subsection{Analysis method}
In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and centro-symmetry parameter(CSP) is used to differ grain boundaries from  $\alpha_2$ phase and $\gamma$ phase. The definition of CSP is as following:

	\begin{equation} \label{eq:csp} 
	P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+{\vec{R}}_{i+6}|^2
	\end{equation}

where $\vec{R_i}$ and ${\vec{R}}_{i+6}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice. The centro-symmetry parameter(CSP) is zero for atoms in a perfect lattice. In other words, if the lattice is distorted, the value of P will not be zero. Instead, the parameter will have a value within the range corresponding to a particular defect. By removing all the perfect and surface atoms within the bulk, atoms around defected zone are visualized.

\section{Results and Discussion}\label{section:RD}

@@

% Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
\subsection{Deformation Mechanism of Two Phase TiAl Alloy without voids}
Snapshots of atom configuration at the 3 of 10 key points are shown by Fig. \ref{fig:Defect}.  Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig. \ref{fig:Defect}(a) and (b),\ $\alpha_2$ phase and defects inside grains have been left. Similarly, $\gamma$ phase grain have been removed in Fig. \ref{fig:Defect}(c) and (d), the defects of $\alpha_2$ phase have been left.  The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of material is under typical elastic deformation, the size of simulation box enlarged due to the loading. In this stage, deformation of the two phase are compatible. Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}. A  great number of dislocation emitted inside $\gamma$ phase at earlier part of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} is shown by Fig. \ref{fig:Defect}(c).  
\begin{figure}[ht] 
	\centering
	\includegraphics[width=1\linewidth]{img/def-box}
	\caption{Microstructure evolution inside $\gamma$ phase(a,b), $\alpha_2$ phase(c,d) during yield stage}
	\label{fig:Defect}
\end{figure}
Experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}. The brittleness of two phase Ti-Al alloy attributed to the poor mobility of dislocation at room temperature. Velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as:
\begin{equation}\label{eq:temp-dis}
v = v_0\ e^{-\Delta H(\tau^*)/kT}
\end{equation}
where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ represents the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions. The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation (\ref{eq:temp-dis}), normalized velocity of dislocation motion is shown by Fig. \ref{fig:temp}. The  velocity  of dislocation movement rise along with increase of  stress, the mobility  of dislocation is relatively poor at 298 K. Due to motion of dislocations is inactive inside $\alpha_2$ phase,  typical strengthening mechanism closely related with interaction between grain boundary and dislocation can not be dramatic at room temperature, piling up of dislocations is not observed in this simulation, which is shown in Fig. \ref{fig:Defect}.
\begin{figure}[ht]
	\centering
	\begin{minipage}{0.495\textwidth}
		\includegraphics[width=1\linewidth]{img/temp}
		\centering
		\caption{Normalized velocity of dislocation motion under different loading conditions}
		\label{fig:temp}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.495\textwidth}		
		\includegraphics[width=1\linewidth]{img/dis-summary}
		\centering
		\caption{Summary of didderent types of dislocation under different strain }
		\label{fig:disum}
	\end{minipage}
\end{figure}

>>>>

% Authors, for the paper (add full first names)
%\Author{Author \orcidA{}}
\Author{Ruicheng Feng$^{1,2}$\orcidA{}; Maomao Wang $^{1,*}$\orcidB{}; Haiyan Li$^{1,*}$; Yongnian Qi$^{1}$; Qi Wang$^{1}$; Zhiyuan Rui$^{1,2}$}

% Authors, for metadata in PDF
%\AuthorNames{ }
% frcly@163.com(R.F.);15620864891@163.com(M.W.); y5217@163.com(H.L.);13893591491@163.com(Y.Q.);18350122524@163.com(Q.W);zhiy_rui@163.com(Z.R)
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
%$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com (R.F.); 15620864891@163.com (M.W.)\\
$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com(R.F.); 15620864891@163.com(M.W.); y5217@163.com(H.L.); 13893591491@163.com(Y.Q.); 18350122524@163.com(Q.W); zhiy\underline{ \ }rui@163.com(Z.R.)\\
% $^{2}$ \quad Key Laboratory of Digital Manufacturing Technology and Application, Ministry of Education, Lanzhou University of Technology, Lanzhou 730050, China
%*; e-mail@e-mail.com}
$^{2}$ \quad State Key Laboratory of Advanced Processing and Recycling of Non-ferrous Metals, Lanzhou University of Technology, Lanzhou 730050, China}
% Contact information of the corresponding author
\corres{Correspondence: 15620864891@163.com; y5217@163.com}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Cold deformation behavior of polycrystalline metallic material is affected by intrinsic defects such as dislocation, void, inclusion etc.  Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy cover about deformation behavior mainly on macro scale. This paper focuses on the cold deformation mechanism of two phase Ti-Al alloy at micro scale, and  the role of void  in deformation process. Molecular dynamics simulations were performed to study the evolution of micro structure of material under uniaxial tension. Interaction between spherical nano void with different size and position was also examined in the simulation. The results show that (1) In elastic stage, deformation of the two phase is coordinated, but $\rm{Ti_3Al}$ is more deformable;(2) In plastic stage, $\gamma$ phase is the major dislocation  source in two phase alloy; (3) void detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
% Keywords
\keyword{two phase Ti-Al alloy; void; molecular dynamics; cold deformation}

@@

\section{Introduction}
% and brittle rapture failure 
Titanium  aluminum based intermetallic alloys are promising high temperature structural materials because of their great corrosion resistance and strength at high temperature. Compared with nickel based alloy,  Ti-Al based alloys have lower density, it can be used in combustion engine, turbine, and other components working at high temperature from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}. The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased from 30\% to 40\% \cite{Bewlay2016}. With the advancement of non-ferrous metallurgy, Ti-Al based alloy components have better economic efficiency than ever before. Ti-Al based alloys have good prospects for applications in aerospace and automobile industry. 
Poor ductility of Ti-Al alloy  at room temperature strongly affects the safety of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.

Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the poor ductility and damage tolerance.  Much of the work has been performed on single phase $\gamma$-TiAl, $\rm{Ti_3Al}$ alloys, and polysynthetically twinned crystals(PTC)\cite{Appel2016}. Experiments reveals that  the dominant deformation mode in $\rm{Ti_3Al}$ at low temperature is slip activity without any twinning, and fracture type is cleavage\cite{sastry1980plastic}. Around 1990s, experimental studies on the two phase lamellae Ti-Al alloys show that  mechanical twin and glide of  dislocation are major sources of deformation\cite{Farenc1993,Appel2005,Appel1998a}. Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale, defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}.Mess research  cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}. In situ experiments have shown that TiAl and $\rm{Ti_3Al}$ in two phase alloy exhibit different properties comparing in single phase alloys\cite{Singh2006}. void can be arose due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen. It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}. The initiation of crack at microscopic scale is a dynamic process, which results in difficulties on study of  mechanism about deformation and cracking, these defects are known playing a fundamental role in the deformation of materials. Multiscale method has been applied to study deformation behavior of polycrystal with single aluminum \cite{Groh2009} and titanium element respectively \cite{Liu2018}. It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.

The effect of void is another great concern about properties and deformation mechanism  of TiAl alloy.  Therefore, it is necessary to study the deformation response of intermetallics structural materials with the consideration of microstructure evolution. Previous study on void growth in single crystal $\gamma$-TiAl reveals that void with high volume fraction detracts yield strength \cite{Tang2014, Xu2011}. Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations, \cite{Jing2018a,Elkhateeb2018}, voids inside material are sources of dislocation and affects the properties of materials differently because of differences in size and position.  The deformation and fracture mechanisms in the duplex microstructure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}. It reveals that existence of voids alone may contribute to strain hardening because they are barriers to dislocation movement in ductile fcc structure metal\cite{Xiong2015}. However, few literature covers about deformation mechanism of two phase Ti-Al alloy and the role of void in atomic scale. Defects are inevitable as micro-pores and loosen from casting, and in the actual work environment with radiation. A lot of work carried out on the  effect of various defects on the behavior of different materials, showing that point defects may affect the properties of materials greatly. The mechanical performance of irradiated copper is affected by the interaction between irradiation and dislocation \cite{Kiener2011b}. Vacancy concentration in single crystal and polycrystal Fe–40 at. Al bulk results in an increase of strength \cite{Yang1998}. Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are sensitive to the existence of void. Surface defects such as small notches can cause low and high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$-TiAl is also lowered by point defect \cite{Wu2016}. The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was reduced due to earlier crack initiation.  The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small cracks in the damaged zone. Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become an effective method to investigate micro deformation mechanism. Defects such as grain boundary, void and segregation play significant roles in the process of fracture \cite{Larsen2016}. This paper focus on the evolution of microstructure, tending to find out its connection to cold deformation behavior of two phase TiAl alloy. MD simulation including model creation and analysis method is given in Section \ref{section:method}, Results and discussion are in Section \ref{section:RD}.

@@

The interaction of particles in the material is determined by interatomic potential. Many reported simulation cases of deforming and crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015,Zepeda-Ruiz2017,Fan2018a}. Embedded atom method (EAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study. The simulation is performed  with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}. We did constant-pressure and constant-temperature (NPT) MD simulation at room temperature (298K). Definition of the potential is as following:

@@

\subsection{Modeling}
\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{img/modeling}
	\caption{Unit cell of \rm{TiAl} (a), $\rm{Ti_3Al}$ (b) and two phase Ti-Al model (c)}
	\label{fig:tial-cell}
\end{figure}

@@

Two phase Ti-Al alloy is composed of $\gamma $-TiAl and $\alpha_2$-$\rm Ti_3Al$, TiAl has a fcc type cell with an $L1_0$ structure, and $\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig. \ref{fig:tial-cell}. Geometry parameters of the two type of unit cell are given by table \ref{tab:lattice_parameter}. Periodic boundary conditions (PBC) were applied along three directions, which makes polycrystal with periodic nanovoid structures. The initial size of simulation box is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model  about 460,000 atoms. The model includes 6 grains, with random shape and orientation created by Voronoi method. Total simulation time is restricted to computer power, thus strain rate in molecular dynamic simulation is much greater than physical experiments. Attempts have been done to find decent time step and strain rate for tensile test with MD simulation. If the strain rate is too high and time step is too large in the simulation, the model cannot predict the real behavior of dislocations.  Previous work \cite{Zhu2008,Wu2016}  reveals that a strain rate from  $10^8\ \rm{s}^{-1}$ to $10^9\ \rm{s}^{-1}$ is appropriate for system composed of metal atoms like Ti-Al metallic materials. Thus the strain rate of uniaxial loading was set as $5\times10^8\ \rm{s}^{-1}$.

% In order to study the deformation mechanism of the two phase alloy and the effect of void, three types of models were created: Type-1.model without any void; Type-2. models with different size void inside $\alpha_2$ phase; Type-3. models with void at $\alpha_2-\gamma$ interface. \ref{tab:lattice_parameter}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure .
\subsection{Analysis method}
In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010}.Dislocation is visualized by DXA method, and centro-symmetry parameter(CSP) is used to differ grain boundaries, $\alpha_2$ phase grains and $\gamma$ phase grains. The definition of CSP is as following:
	\begin{equation} \label{eq:csp} 
	P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+{\vec{R}}_{i+6}|^2
	\end{equation}
where $\vec{R_i}$ and ${\vec{R}}_{i+6}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice. The centro-symmetry parameter(CSP) is zero for atoms in a perfect lattice. In other words, if the lattice is distorted, the value of P will not be zero. Instead, the parameter will have a value within the range corresponding to a particular defect. By removing all the perfect and surface atoms within the bulk, atoms around defected zone are visualized. 
 \subsection{Model Verification}
The results of molecular dynamics simulation greatly rely on accuracy of potential and controlling parameters such as strain rate, temperature and relaxation time. Thus we performed model verification on a simplified model and then compared the results with experiments and simulation done by others.
 \begin{figure}[ht]
 	\centering
 	\includegraphics[width=1\linewidth]{img/cold-fracture2}
 	\caption{(a) Verifying model: TiAl single crystal bulk (b) Cracked surface of atomic model\\ (c) Cracked surface from experiment\cite{CHEN2015365}}
 	\label{fig:verify}
 \end{figure}
 uniaxial tensile loading  was applied to single crystal $\gamma$-TiAl bulk shown by Fig. \ref{fig:verify}(a), potential and relaxation parameters are as same as which applied to the polycrystalline model. When temperature is 300K, the sample was tensioned along [0 0 1] direction at a constant stain rate of $5\times10^8\ \rm{s}^{-1}$. The yield strength of the single crystal TiAl alloy is 9.5 GPa  and that is in good agreement with  work by Tang\cite{Tang2010} in consideration of size effect. And the snapshoot of the fracture surface is shown by Fig. \ref{fig:verify}, and compared with experiment results by Cao\cite{CHEN2015365} shown in Fig. \ref{fig:verify}(c). It should be noticed that the image from SEM is in a greater scale than our simulation cell. However, the cracked surface in atomic model exhibits two major characteristics of TiAl alloy. First, the fracture type of TiAl at room temperate is typical brittle failure. Second, the fracture surface  of atomic model in Fig. \ref{fig:verify} (b) is typical cleavage surface. This verification case has proven that the EAM potential is efficiency and accurate enough, and the simulation work flow is valid to predict failure behavior of  the system composed of Ti-Al.
\section{Results and Discussion}\label{section:RD}

@@

\subsection{Deformation Mechanism of Two Phase Ti-Al Alloy }

% Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
% \subsection{Plastic }
During elastic stage, the deformation of $\alpha_2$ phase and $\gamma$ phase grains is compatible, however the properties of two phases are different. The elastic constants given by  experiments\cite{Schwarz1995,Tanaka1996} are listed in  table \ref{tab:elastic}. $C_{11}^{\alpha_2}$ is 176, which is smaller than $C_{11}^{\gamma}$, other 5 parameters but $C_{33}$ of $\rm{Ti_3Al}$ are also smaller than TiAl. In order to quantify the difference of the two phase, deformation gradient was calculated by formulation:
\begin{equation}
\label{eq:strain-grade}
\mathbf { F^e } = \frac { \partial \mathbf { x } } { \partial \mathbf { X } } = \operatorname { Grad } \mathbf { x } , \quad F _ { i J } = \frac { \partial x _ { i } } { \partial X _ { J } }
\end{equation}
we computes the atomic level elastic strain and deformation gradient tensors in crystalline systems with the numerical method proposed by \cite{Singh2006}. When global strain is 0.015, local elastic strain $F_{xx}$ of the model is measured along the line cross center of the model and shown by Fig. \ref{fig:strain}. In te figure, $\alpha_2$ phase located in the central part of the axial, and other parts on the axial are $\gamma$ phase.  It should be noticed that atomic level elastic strain effected by random thermal displacements of atoms, thus fluctuation value exists in Fig. \ref{fig:strain}. The local strain of $\alpha_2$ phase grain is greater than $\gamma$ phase grain when global strain of model is 0.015. From the value of local strain we can conclude that $\gamma$ phase less deformable than $\alpha_2$ phase during elastic stage.
\begin{figure}[ht]
	\centering
	\includegraphics[width=0.75\linewidth]{img/strgrad}
	\caption{Local strain along tensile direction }
	\label{fig:strain}
\end{figure}

\begin{table}[ht]
	\caption{Elastic constants of TiAl and $\rm{Ti_3Al}$}
	\centering
	\begin{tabular}{l c c c c c c c c c c}
		\toprule
		\textbf{ } &$C_{11}$ &$C_{12}$ &$C_{13}$ &$C_{33}$ &$C_{44}$ &$C_{66}$\\		 
		\midrule
		TiAl\cite{Schwarz1995} &186 &72 &74 & 176 &101 &77	 \\
		\midrule
		% Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.Fu = sin20 & 0.21 & 0.22 & 0.23 \\
		% \midule
		$\rm{Ti_3Al}$\cite{Tanaka1996}	& 176 &  87.8 & 61.2 & 218.7 & 91.9 & 62.4   \\
		\bottomrule
	\end{tabular} 
	\label{tab:elastic}
\end{table}
%\begin{equation}
%	\label{eq:strin-grade2}
%		\mathbf{e} = 1 / 2 \left[ I - \left( \mathbf{F ^ { e }} \right) ^ { - T } \left(\mathbf{ F ^ { e }} \right) ^ { - 1 } \right]
%\end{equation}
%\begin{equation}
%\begin{aligned} d $\mathbf { x } & = \frac { \partial \mathbf { x } } { \partial \mathbf { X } } d \mathbf { X } \\ & = \nabla \chi ( \mathbf { X } , t ) d \mathbf { X } = \mathbf { F } ( \mathbf { X } , t ) d \mathbf { X }$
%\end{aligned} 
%\end{equation}
Snapshots of atoms configuration at the 3 of 10 key points are shown by Fig. \ref{fig:Defect}.  Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig. \ref{fig:Defect}(a) and (b),\ $\alpha_2$ phase and defects inside grains have been left. Similarly, $\gamma$ phase grain have been removed in Fig. \ref{fig:Defect}(c) and (d), the defects of $\alpha_2$ phase have been left.  The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of material is under typical elastic deformation, the size of simulation box enlarged due to the loading. In this stage, deformation of the two phase are compatible. Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}. A  great number of dislocation emitted inside $\gamma$ phase at earlier part of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} is shown by Fig. \ref{fig:Defect}(c).  
\begin{figure}[ht] 
	\centering
	\includegraphics[width=1\linewidth]{img/def-box}
	\caption{Microstructure evolution inside $\gamma$ phase(a,b), $\alpha_2$ phase(c,d) during yield stage}
	\label{fig:Defect}
\end{figure}
Experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}. The brittleness of two phase Ti-Al alloy attributed to the poor mobility of dislocation at room temperature. Velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as:
\begin{equation}\label{eq:temp-dis}
v = v_0\ e^{-\Delta H(\tau^*)/kT}
\end{equation}
where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ represents the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions. The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation (\ref{eq:temp-dis}), normalized velocity of dislocation motion is shown by Fig. \ref{fig:temp}. The  velocity  of dislocation movement rise along with increase of  stress, the mobility  of dislocation is relatively poor at 298 K. Due to motion of dislocations is inactive inside $\alpha_2$ phase,  typical strengthening mechanism closely related with interaction between grain boundary and dislocation can not be dramatic at room temperature, piling up of dislocations is not observed in this simulation, which is shown in Fig. \ref{fig:Defect}.
\begin{figure}[ht]
	\centering
	\begin{minipage}{0.495\textwidth}
		\includegraphics[width=1\linewidth]{img/temp}
		\centering
		\caption{Normalized velocity of dislocation motion under different loading conditions}
		\label{fig:temp}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.495\textwidth}		
		\includegraphics[width=1\linewidth]{img/dis-summary}
		\centering
		\caption{Summary of didderent types of dislocation under different strain }
		\label{fig:disum}
	\end{minipage}
\end{figure}
